### 2025-01-25 our_article/MCM_article/article_file.tex
更新了论文

        \subsection{Notations}
      % table
      \begin{table}[H]
        \centering
        % \caption{An example of a three-line table.}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $\mathbf{X}$ & Vector $[N_w,N_c,N_p,N_b,N_B,C_{hc},C_{pc}]^T$ to describe the system,etc. \\
          $wd$ & Subscription for weeds \\
          $crp$ & Subscription for crops \\
          $pst$ & Subscription for pest(who consumes crops) \\
          $ins$ & Subscription for other insects(who consume weeds) \\
          $bd$ & Subscription for small birds(herbivorous) \\
          $Bd$ & Subscription for huge birds(carnivorous) \\
          $bt$ & Subscription for bats \\
          $snk$ & Subscription for snake \\
          $frg$ & Subscription for frog \\
          $HC$ & Subscription for herbicide \\
          $PC$ & Subscription for pesticide \\
          $C_i$ & Concentration of certain chemical \\
          $N_i$ & Numbers of certain species \\
          $W_i$ & Biomass of certain species \\
          $w_i$ & Mass of individuals \\
          $r_i$ & Natural growth gate of certain species\\
          $K_i$ & Carrying capacity of certain species\\
          $\alpha$ & The effect of chemical concentration on growth rate\\
          $\beta$ & Interspecific competition factor\\
          $\gamma$ & Activity of decomposer\\

@@

  % \section{Models}
  %       % figure
  %   \begin{figure}[ht]
  %     \centering
  %     \includegraphics[width=0.5\linewidth]{images/energy_flow.png} % 替换为你的第一张图片路径
  %     \caption{Energy Flow}
  %     \label{fig:EnergyFlow}
  %   \end{figure}

>>>>

        \subsection{Notations}
      % table
      \begin{table}[H]
        \centering
        % \caption{An example of a three-line table.}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $\mathbf{X}$ & Vector $[N_{wd},N_{crp},N_{pst},N_{ins},...,C_{hc},C_{pc}]^T$ to describe the system,etc. \\
          $wd$ & Subscription for weeds \\
          $crp$ & Subscription for crops \\
          $pst$ & Subscription for pest(who consumes crops) \\
          $ins$ & Subscription for other insects(who consume weeds) \\
          $bd$ & Subscription for small birds(herbivorous) \\
          $Bd$ & Subscription for huge birds(carnivorous) \\
          $bt$ & Subscription for bats \\
          $snk$ & Subscription for snake \\
          $frg$ & Subscription for frog \\
          $HC$ & Subscription for herbicide \\
          $PC$ & Subscription for pesticide \\
          $C_i$ & Concentration of certain chemical \\
          $N_i$ & Numbers of certain species \\
          $W_i$ & Biomass of certain species \\
          $w_i$ & Mass of individuals \\
          $r_i$ & Natural growth gate of certain species\\
          $K_i$ & Carrying capacity of certain species\\
          $\alpha$ & The effect of chemical concentration on growth rate\\
          $\beta$ & Interspecific competition factor\\
          $\gamma$ & Activity of decomposer\\

@@

  \section{Models}
    %     % figure
    % \begin{figure}[ht]
    %   \centering
    %   \includegraphics[width=0.5\linewidth]{images/energy_flow.png} % 替换为你的第一张图片路径
    %   \caption{Energy Flow}
    %   \label{fig:EnergyFlow}
    % \end{figure}
    \subsection{NGLG(Natrual Growth Leslie-Gower) Model}
      \subsubsection{Leslie-Gower Model}
        Ecosystem components are complex and interdependent. 
        In the simplest case, when climate, soil, and other conditions are favorable, only biological factors shuold be considered. 
        If the population sizes of producers, primary consumers, and secondary consumers are used to describe the entire system, 
        the Leslie-Gower Model, as described by \cite{GUO20142850}, can be applied.
        \begin{equation}
          \left\{ \begin{array}{c}
            \frac{\mathrm{d}N_1\left( T \right)}{\mathrm{d}T}=r_1N_1\left( T \right) \left( 1-\frac{N_1\left( T \right)}{K_1} \right) -\alpha _1N_2\left( T \right) ,\\
            \frac{\mathrm{d}N_2\left( T \right)}{\mathrm{d}T}=r_2N_2\left( T \right) \left( 1-\frac{N_2\left( T \right)}{c_1X\left( T-\tau _1 \right)} \right) -\alpha _2Z\left( T \right) ,\\
            \frac{\mathrm{d}N_3\left( T \right)}{\mathrm{d}T}=r_3N_3\left( T \right) \left( 1-\frac{N_3\left( T \right)}{c_2N_2\left( T-\tau _2 \right)} \right)\\
          \end{array} \right. 
        \end{equation}
        In the equations,$N_1,N_2,N_3$ represents producers, primary consumers, and secondary consumers, respectively; 
        $c_1>0$ and $c_2>0$ are the measure of food quality measure that prey provides for conversion into the births of consumer and predator; 
        the positive parameters $a_1$ and $a_2$ are the predation rate of consumer and predator; 
        two delays $\tau_1, \tau_2>0$ are introduced for digestion periods corresponding to consumer-eat-resource and predator-eat-consumer, 
        which are called the resource digestion delay (RDD) and consumer digestion delay (CDD), respectively.
        It is a schematic diagram of this model.
      \subsubsection{NGLG Model}
